Incentivizing Exploration with Heterogeneous Utilities

### 2017-11-24 paper.tex
did some edits

If our algorithm decides to incentivize an arm $i$, it uses the ``pay whatever it takes'' strategy in which the payment offered is $\max_{\theta,j} \theta \cdot (u_j - u_i)$. This maximum over $\theta$ is taken over the support of $F$, which we recall is assumed compact.  (We use this ``pay whatever it takes'' strategy for its simplicity, and in Section~\ref{sec:pi} we provide an alternate and smaller incentive payment that achieves the same payment budget bound and regret bound).

@@

Intuitively, assumption~\ref{A1} states that there are not many agents who are indifferent between their best arm and the second best arm. For simplicity in our analysis, we use a slightly stronger condition below: $M=\max_{i,j}sup_{y\in R^{+}}f_{i,j}(y) <\infty$.  \pfcomment{Let's state the assumption in terms of $M$, which is what our proof uses, and then if you want to say that we can also show similar results for $M'$ we can say that informally here.}

>>>>

If our algorithm decides to incentivize an arm $i$, it uses the ``pay whatever it takes'' strategy in which the payment offered is $\max_{\theta,j} \theta \cdot (u_{j,t} - u_{i,t})$. This maximum over $\theta$ is taken over the support of $F$, which we recall is assumed compact.  (We use this ``pay whatever it takes'' strategy for its simplicity, and in Section~\ref{sec:pi} we provide an alternate and smaller incentive payment that achieves the same payment budget bound and regret bound).

@@

Intuitively, assumption~\ref{A1} states that there are not many agents who are indifferent between their best arm and the second best arm.
